Optimal (Multiway) Spatial Joins

### 2024-05-27 msj.tex
yufei

\begin{figure*}
    \begin{tabular}{cccc}
        \hspace{-5mm}
        \includegraphics[height=45mm]{./artwork/alg-ex1-a} &
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex1-b} & 
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex1-c} &
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex1-d} \\ 
        \hspace{-5mm} (a) $R_1$, $R_2$, $H$, and $V$ &
        \hspace{-4mm} (b) $R_1'$ and $R_2'$ &
        \hspace{-4mm} (c) $R_1'$, $R_2'$, $H$, and $V$ &
        \hspace{-4mm} (d) $R_1^*$, $R_2^*$ ($= \emptyset$), $H$, and $V$
    \end{tabular}
    \figcapup 
    \caption{Finding H-V $k$-SJ result tuples of type 1 ($k = 4$)} 
    \label{fig:hv:type1:ex}
    \figcapdown 
\end{figure*}

@@

\extraspacing {\underline{\em Example 4.5.} The two tuples $\bm{t}_1 = (\alpha', \beta_1')$ and $\bm{t}_2 = (\alpha', \beta_2')$ in $\J(R_1',$ $R_2')$ satisfy $\gbot(\bm{t}_1) = \gbot(\bm{t}_2) = \alpha'$. Therefore, $\maxtop(\alpha') = \max\{\ytop(B_{\bm{t}_1}), \ytop(B_{\bm{t}_2})\} = \max\{6, 9.5\} = 9.5$. The top-sliced rectangle of $r'$ is the rectangle $\alpha^*$ in Figure~\ref{fig:hv:type1:ex}d. Rectangles $\beta'_1$ and $\beta'_2$ do not have top-sliced rectangles.
\qed

@@

>>>>

\begin{figure*}
    \begin{tabular}{cccc}
        \hspace{-5mm}
        \includegraphics[height=45mm]{./artwork/alg-ex1-a} &
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex1-b} & 
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex1-c} &
        \hspace{-4mm}
        \includegraphics[height=45mm]{./artwork/alg-ex1-d} \\ 
        \hspace{-5mm} (a) $R_1$, $R_2$, $H$, and $V$ &
        \hspace{-4mm} (b) $R_1'$ and $R_2'$ &
        \hspace{-4mm} (c) $R_1'$, $R_2'$, $H$, and $V$ &
        \hspace{-4mm} (d) $R_1^*$, $R_2^* = \emptyset$, and $H$ 
    \end{tabular}
    \figcapup 
    \caption{Finding H-V $k$-SJ result tuples of type 1 ($k = 4$)} 
    \label{fig:hv:type1:ex}
    \figcapdown 
\end{figure*}

@@

\extraspacing {\underline{\em Example 4.5.} Recall from Example 4.3 that rectangle $\alpha'$ serve as both $\gbot(\bm{t}_1)$ and $\gbot(\bm{t}_2)$. Thus, $\maxtop(\alpha') = \max\{\ytop(B_{\bm{t}_1}),$ $\ytop(B_{\bm{t}_2})\} = \max\{6, 9.5\} = 9.5$. The top-sliced rectangle of $r'$ is the rectangle $\alpha^*$ in Figure~\ref{fig:hv:type1:ex}d. Rectangles $\beta'_1$ and $\beta'_2$ do not have top-sliced rectangles.
\qed

@@

\extraspacing {\underline{\em Example 4.6.}} It is clear from Figure~\ref{fig:hv:type1:ex}d that $\cross_H(\alpha^*)$ contains $h_2, h_4$, and $h_5$, sorted in ascending order of y-coordinate. Recall that 
$\gbot(\bm{t}_1) = \gbot(\bm{t}_2) = \alpha'$. Both $\dcross_H(\bm{t}_1) = \set{h_2}$ and $\dcross_H(\bm{t}_2) = \set{h_2, h_4, h_5}$ are prefixes of the sorted list.
\qed
